Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-13 csf-2017/paper.tex
bibstyle from plain to plainnat
Related work typos

The idea of applying SKLRs to an assembly language was applied before by
\citet{Hur:2011:KLR:1926385.1926402}, who constructed a binary SKLR for
formulating and proving correctness of an ML-to-assembly compiler. Their
condition on the assembly code are quite loose (for example, they allow
hand-written and self-modifying assmebly code), but they do assume code that it
is non-adversarial and respects the ABI of the high-level language (for example,
the code does not store return pointers and invoke them after their intended
lifetime). As a result, they can treat return pointers as evaluation contexts in
a lambda calculus and use biorthogonality~\cite{pitts_operational_1998}. This
means that they define the logical relation to accept evaluation contexts if
they produce related observations for related values and to accept terms if they
produce related observations when plugged into related evaluation contexts. In
our setting, there is no guarantee that adversarial code will treat return
pointers as intended, so, as described in Section~\ref{sec:logical-relation}, we
define our logical in a (arguably natural but still) novel way, using a single
orthogonal closure, i.e. accept terms if they produce related observations when
given related arguments, where those arguments include the return pointer.

>>>>

The idea of applying SKLRs to an assembly language was applied before by
\citet{Hur:2011:KLR:1926385.1926402}, who constructed a binary SKLR for
formulating and proving correctness of an ML-to-assembly compiler. Their
condition on the assembly code are quite loose (for example, they allow
hand-written and self-modifying assmebly code), but they do assume code that
is non-adversarial and respects the ABI of the high-level language (for example,
the code does not store return pointers and invoke them after their intended
lifetime). As a result, they can treat return pointers as evaluation contexts in
a lambda calculus and use biorthogonality~\cite{pitts_operational_1998}. This
means that they define the logical relation to accept evaluation contexts if
they produce related observations for related values and to accept terms if they
produce related observations when plugged into related evaluation contexts. In
our setting, there is no guarantee that adversarial code will treat return
pointers as intended, so, as described in Section~\ref{sec:logical-relation}, we
define our logical relation in a (arguably natural but still) novel way, using a single
orthogonal closure, i.e. accept terms if they produce related observations when
given related arguments, where those arguments include the return pointer.
